---
title: "Territory Simulation Analyses"
author: "Thomsen B. Bolton"
date: "2026-06-17"
output: pdf_document
---

```{r Frodo, comment = NA. echo = FALSE}
library(ggplot2)
library(tidyverse)
library(glmmTMB)   
library(mgcv)
library(emmeans)
library(DHARMa)
#library(broom)
library(broom.mixed)
library(caret)
library(ggfortify)
library(effects)
library(factoextra)
library(gridExtra)
library(corrplot)
library(kableExtra)
library(gratia)
library(ggrepel)
df_list <- list()
probs <- read.csv("probs.csv", header = TRUE)
for (i in 1:22) {
  df<- read.csv(paste0("sim_", i, ".csv"), header = TRUE)
  df <- filter(df, Sex == "F")
  df$birdID=factor(df$birdID)
  df$Sex=factor(df$Sex)
  df$Terrs=factor(df$Terrs)
  df$fac.yr=factor(df$Yr)
  # Calculate z-scores within each year
  df <- df %>%
  group_by(fac.yr) %>%
  mutate(
    z_score = (Fledge - mean(Fledge, na.rm = TRUE)) / sd(Fledge, na.rm = TRUE)
  ) %>%
  ungroup()
  df$Eggs <- ifelse(df$Fledge > 0, 1, 0)
  
  df_list[[i]] <- df
}
```

For this report, we generated 20 different simulated data sets varying probability of mate fidelity, a pair's territory fidelity, a single male's territory fidelity, and a single female's territory fidelity. Latin hypercube sampling (LHS) was used to generate these probabilities for the 20 different runs. 

# Simulation 1 

## Number of fledgling as the response (Poisson)

```{r Gandalf, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[1]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Apart from BIC, models that included territory seemed to perform better on the model selection criteria. 
We now also need to check model assumptions and diagnostics.

```{r Boromir, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for and suggest underfitting.  
```{r Gothmog, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```
These model diagnostics seem to suggest a slight violation of assumptions and underfitting.

## Z-score number of fledgling (Gaussian)

```{r Bilbo Baggins, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[1]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Even though AIC and BIC aren't selecting a clear winner, the extremely low adjusted $R^2$ would seem to suggest that models should include territory. 

We now also need to check model assumptions and diagnostics.

```{r Legolas, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect.

```{r Gloin, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```
The QQ plot does suggest violation in the model assumptions. 

## Eggs (Binomial)

```{r Galadriel, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[1]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

The model only fitting only territory as a random effect seems to perform better on AIC and BIC. However the adjusted $R^2$ of the model that includes both variables is noticeably higher than the models that were fit with only one random effect. While one could debate over including both random effects, it does seem safe to say that no practitioner would pick the model that only includes band ID as the random effect.

We now also need to check model assumptions and diagnostics.

```{r King Theoden, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for, it seems there is some underfitting in the model. However, the diagnostic plots don't seem terribly unreasonable. 
```{r Balrog, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 1

```{r Elrond, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[1], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[1], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[1], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[1], 3))
print(string)
```
Seeing that our probability of mate fidelity was so low, it makes sense that models with territory performed well on model selection criteria. However, our dispersal probabilities were not terribly high, so apart from the model that fit z-scores as a response, models with only bird ID weren't substantially worse than the ones fit with territory. 

# Simulation 2

## Number of fledgling as the response (Poisson)

```{r Gollum, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[2]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

It does seem that the model only fitting territory performs well on the model selection criteria, even though its not the best for all of the model selection criteria, there isn't a criteria where it is performing substantially worse than the best model in that criteria, and it does have the best AIC. 

We now also need to check model assumptions and diagnostics.

```{r Fatty Bolger, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for and would suggest some underfitting. However, noe of the diagnostic plots seem to suggest major violation of distributional assumptions. 

```{r Gondor, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Rivendell, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[2]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Apart from BIC, the model fitting both terms is performing the best on selection criteria

We now also need to check model assumptions and diagnostics.

```{r Moria, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

The k-indices are better than all previous models. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem reasonable. 

```{r Sauron, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Thranduil, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[2]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Each model seems to perform well on different selection criteria. I don't feel there is a clear superior model.

We now also need to check model assumptions and diagnostics.

```{r Arwen, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for and suggest possible underfitting. However, the diagnostic plots don't seem terribly unreasonable. 
```{r Minas Morgal, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 2

```{r Thorin, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[2], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[2], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[2], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[2], 3))
print(string)
```
This is a bit surprising since birds were most likely moving around a bit. However, we are analyzing females and the probability of single female dispersal is quite low, which could be playing a role in the fact that territory models aren't clearly better. 

# Simulation 3

## Number of fledgling as the response (Poisson)

```{r Samwise Gamgee, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[3]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
The models fitting territory seem to perform similarly on the selection criteria, except the model that fits both terms does not perform well on BIC. The model fitting band ID only performs well on BIC, thus I would pick the model that only fits territory as a random effect.  

We now also need to check model assumptions and diagnostics.

```{r Mordor, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't look terrible, but they could also be better. 
```{r Grima Wormtongue, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Morgoth, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[3]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

The band ID model did perform well on BIC, but not the other criteria. Seeing that the model that fit both terms has a poor BIC, I would recommend the model only fitting territory. 

We now also need to check model assumptions and diagnostics.

```{r Pippin, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices seem reasonable. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem reasonable except for the first model which only fits band ID as a random effect. This seems reasonable considering we are missing the factor that is driving variation in fledgling success. 

```{r Merry, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Balin, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[3]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

I would say it's somewhat difficult to pick between the models fitting only one random effect. However, the model fitting both REs only performs well on adjusted $R^2$. I would pick the model fitting only territory since it performs better on AIC and adjusted $R^2$ than the model only fitting band ID. 

We now also need to check model assumptions and diagnostics.

```{r Saruman, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 
```{r Haldir, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 3

```{r Everard Proudfoot, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[3], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[3], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[3], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[3], 3))
print(string)
```
Here, we should notice the low mate fidelity rate and the fact that dispersal probabilities aren't terribly low.

# Simulation 4

## Number of fledgling as the response (Poisson)

```{r Smeagol, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[4]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Territory seems to be the best model since it performs competitively on all criteria. 

We now also need to check model assumptions and diagnostics.

```{r The Shire, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots for the models that include territory seem to look reasonable.  

```{r The Witch King of Angmar, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Eowyn, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[4]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Based on AIC and adjusted $R^2$, I would recommend the model fitting both random effects. 

We now also need to check model assumptions and diagnostics.

```{r The Mouth of Sauron, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem reasonable except for the first model which only fits band ID as a random effect. This seems reasonable considering we are missing the factor that is driving variation in fledgling success. 

```{r Rossie Cotton, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Minas Tirith, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 19)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 19)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 19)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[4]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

We are in a situation where yet again, there isn't a model that is clearly better. 

We now also need to check model assumptions and diagnostics.

```{r Lurtz, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 
```{r Elendil, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 4

```{r Ori, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[4], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[4], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[4], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[4], 3))
print(string)
```
Even though probability of mate fidelty was high, so were the probabilities of dispersal, thus allowing a territory effect to seem present. 

# Simulation 5

## Number of fledgling as the response (Poisson)

```{r Sting, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[5]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
From the output above, even though the models with either territory or both terms perform similarly, the BIC on the model with both terms is a bit high, so I would pick the model that only includes territory. 

We now also need to check model assumptions and diagnostics.

```{r Isildur, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Helm's Deep, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Mirkwood, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[5]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

The model with both terms performed best on AIC and adjusted $R^2$. I would most likely pick that model.

We now also need to check model assumptions and diagnostics. 

```{r Eomer, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r Eagles, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Gimili, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[5]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

I don't think there is a model that is clearly better. 

We now also need to check model assumptions and diagnostics.

```{r Cave Troll, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Minas Morgal, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 5

```{r Smaug, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[5], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[5], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[5], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[5], 3))
print(string)
```
Once again, we had low a probability of single female dispersal and it was harder to distinguish the territory effect. 

# Simulation 6

## Number of fledgling as the response (Poisson)

```{r Coruscant, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[6]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
From the output above, I would definitely recommend fitting the model with a band ID random effect. 

We now also need to check model assumptions and diagnostics.

```{r Anakin Skywalker, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Rex, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)
```{r Fives, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[6]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

I would recommend fitting both REs in the model.

We now also need to check model assumptions and diagnostics. 

```{r Padme, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r Chosen one, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Yularen, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[6]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Based on the output alone, I would suspect a band ID effect. 

We now also need to check model assumptions and diagnostics.

```{r Oddball, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Echo, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 6

```{r Jesse, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[6], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[6], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[6], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[6], 3))
print(string)
```
Once again, we had low a probability of single female dispersal and it was harder to distinguish the territory effect. 

# Simulation 7

## Number of fledgling as the response (Poisson)

```{r Cassian Andor, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[7]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Based on the model only including band ID's extremely low adjusted $R^2$, and the other two models similar performance, I would recommend the model only fitting territory. 

We now also need to check model assumptions and diagnostics.

```{r Maarva Andor, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful, except for the model only fitting band ID. I would not trust model output from that model. 

```{r U-wing, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Bix Caleen, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[7]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar to the previous models, I would pick the model only fitting territory. 

We now also need to check model assumptions and diagnostics. 

```{r K-2SO, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices look good. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r B2EMO, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Brasso, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[7]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

The model fitting only territory has a good AIC and adjusted $R^2$, thus it seems the territory effect is present. 

We now also need to check model assumptions and diagnostics.

```{r Ferrix, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable.

```{r Timm, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 7

```{r Melshi, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[7], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[7], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[7], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[7], 3))
print(string)
```
All probabilities of dispersal were high and the territory effect was pretty clear on these sets of models. 

# Simulation 8

## Number of fledgling as the response (Poisson)

```{r Sheev Palpatine, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[8]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
All models are performing similarly. I wouldn't think there to be one effect that is stronger than the other based on the output above, 

We now also need to check model assumptions and diagnostics.

```{r Moff Jerjerrod, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Death Star, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Imperial Senate, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[8]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

I would potentially be more partial to a band ID effect due to the low adjusted $R^2$ on the territory only model and the fact that the territory only model has the worst AIC. 

We now also need to check model assumptions and diagnostics. 

```{r Thrawn, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r Chancellor, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Exegol, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[8]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

I would say something similar to what I said on the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r Sith Eternal, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Royal Guards, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 8

```{r Lighting, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[8], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[8], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[8], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[8], 3))
print(string)
```
W had a low probability of male dispersal and the territory effect was difficult to detect. 

# Simulation 9

## Number of fledgling as the response (Poisson)

```{r Jabba the Hutt, comment= NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[9]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
From the output above, there doesn't seem to be a clear domminant effect.  

We now also need to check model assumptions and diagnostics.

```{r Bossk, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. It also seems that models with bandID are shrinking the year smoother out of the model. The diagnostic plots are not ideal. I would be more cautious with these models. 

```{r Boba Fett, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Bib Fortuna, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[9]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar to the batch of models before.

We now also need to check model assumptions and diagnostics. 

```{r Gamorean Guard, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r Sy Snootles, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Max Rebo, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[9]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

The models with band ID seem to to better on AIC and adjusted $R^2$. 


We now also need to check model assumptions and diagnostics.

```{r Wooof, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Tatooine, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 9

```{r Desert skiff, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[9], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[9], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[9], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[9], 3))
print(string)
```
Once again, we had low a probability of single female dispersal and it was harder to distinguish the territory effect. 

# Simulation 10

## Number of fledgling as the response (Poisson)

```{r Han Solo, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[10]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
One could argue between fitting both effects or just territory, but the band ID only model does not seem to perform as well. 

We now also need to check model assumptions and diagnostics.

```{r Chewbacca, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r DL-44, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Millenium Falcon, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[10]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Based on AIC and adjusted $R^2$, I would say the model fitting both random effects performs the best. 

We now also need to check model assumptions and diagnostics. 

```{r Corellia, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots all seem somewhat reasonable.  

```{r Beckett, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Lando, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[10]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

I don't think there is a model that is clearly better. 

We now also need to check model assumptions and diagnostics.

```{r Rio Durrant, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Kessel run, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 10

```{r Qi'ra, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[10], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[10], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[10], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[10], 3))
print(string)
```
Male and pair dispersal probabilities were low, but female dispersal were moderate. In the models, there was more of a preference towards a territory effect, but it wasn't terribly clear. 

# Simulation 11

## Number of fledgling as the response (Poisson)

```{r Rey, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[11]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Overall, I wouldn't say there's a clear superior model when considering multiple selection criteria. 

We now also need to check model assumptions and diagnostics.

```{r Finn, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Porgs, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Jakku, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[11]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Seeing as the model with both terms has the best AIC and a higher adjusted $R^2$, I would recommend that model.

We now also need to check model assumptions and diagnostics. 

```{r Poe Dameron, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The QQ plots for the models including territory are better, but none of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r BB-8, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Holdo, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[11]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r Crait, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Maz Kanata, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 11

```{r Scavenger, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[11], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[11], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[11], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[11], 3))
print(string)
```
Two of our dispersal probabilities were low and mate fidelity wasn't low either, which makes sense as to why there isn't a clear territory effect. 


# Simulation 12

## Number of fledgling as the response (Poisson)

```{r Darth Maul, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[12]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
The model only fitting territory as a random effect seems to perform well on the criteria, while the other models don't perform well on all criteria. 

We now also need to check model assumptions and diagnostics.

```{r Dathomir, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps a bit concerning. I would be more hesitant to trust these models. 

```{r Mother Talzin, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Merrin, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[12]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics. 

```{r Savage Oppress, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The QQ plots for the models including territory are better, but none of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r Karis, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Crimson Dawn, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[12]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r Shadow Collective, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Dryden Vos, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 12

```{r Pre Vizsla, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[12], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[12], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[12], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[12], 3))
print(string)
```
Since there was a low probability of mate fidelity and a moderate probabiolity of female dispersal, there did seem to be a territory effect present here. 

# Simulation 13

## Number of fledgling as the response (Poisson)

```{r Luke Skywalker, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[13]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Based on AIC and adjusted $R^2$, I would recommend the territory only model. 

We now also need to check model assumptions and diagnostics.

```{r Beru Lars, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful, except for the model only fitting band ID. 

```{r Binary Sunset, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Dagobah, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[13]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar reasoning as the previous batch of models except for the model with both terms.

We now also need to check model assumptions and diagnostics. 

```{r Ben Kenobi, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices look okay. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The QQ plots for the models including territory are better, but none of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r Owen Lars, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Yoda, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[13]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r X-wing, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Yavin, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 13

```{r Red 5, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[13], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[13], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[13], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[13], 3))
print(string)
```
This run had moderate to high probabilities of dispersal and low mate fidelity probabilities and the territory effect seemed pretty detectable. 

# Simulation 14

## Number of fledgling as the response (Poisson)

```{r Count Dooku, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[14]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Based on AIC and adjusted $R^2$, I would say the model fitted only with territory seems to perform the best. 

We now also need to check model assumptions and diagnostics.

```{r Nute Gunray, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, excpet for the model with band ID as the RE.

```{r General Grievous, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Wat Tambor, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[14]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar for the previous batch of models

We now also need to check model assumptions and diagnostics. 

```{r B1, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. Diagnostic plots look okay. 

```{r B2, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Ventress, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[14]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Even though the adjusted $R^2$ for the model containing both REs is a bit higher, the AIC and BIC for that model are not great. If only one model could be used, I would recommend the territory model. 

We now also need to check model assumptions and diagnostics.

```{r Sereno, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable.

```{r Poggle the Lesser, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 14

```{r Geonosis, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[14], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[14], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[14], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[14], 3))
print(string)
```
All probabilities seem pretty moderate apart from probability of single male dispersal. 

# Simulation 15

## Number of fledgling as the response (Poisson)

```{r Mon Mothma, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[15]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
The model with only territory is performing well on all criteria. 

We now also need to check model assumptions and diagnostics.

```{r Vel Sartha, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, except for the model with only band ID as a random effect. 

```{r Wedge Antilles, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Biggs, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[15]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

While there could be a debate between including band ID in the model, I would recommend one of the models with territory. 

We now also need to check model assumptions and diagnostics. 

```{r Frissk, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices seem okay. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The QQ plots for the models suggest a bit of a skew.

```{r Bail Organa, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Raddus, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[15]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

The model with territory as the random effect seems to do okay on the criteria. However, I don't think it's super clear which model is best.  

We now also need to check model assumptions and diagnostics.

```{r Ackbar, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Crix Madine, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 15

```{r Y-wing, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[15], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[15], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[15], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[15], 3))
print(string)
```
I do find it interesting that the probability of single female is so low. That has seemed to be associated with difficulties detecting the territory only effect. 

# Simulation 16

## Number of fledgling as the response (Poisson)

```{r Darth Vader, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[16]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
I would recommend the model that only fits territory as a random effect based on the output above.  

We now also need to check model assumptions and diagnostics.

```{r Tie advanced, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Executor, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Tarkin, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[16]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Because of the high BIC of the model fitting both REs, I would most likely recommend the model only fitting territory as a random effect. However, the adjusted $R^2$ of the model fitting both REs is quite a bit higher. 

We now also need to check model assumptions and diagnostics. 

```{r Piett, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices look pretty good. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The QQ plots for the models including territory are better, but none of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r Veers, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Devastator, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[16]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r Ozzel, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r Storm trooper, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 16

```{r Mustafar, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[16], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[16], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[16], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[16], 3))
print(string)
```
With moderate probabilities for both female dispersal and mate fidelity, it did seem that we could see a bit of a territory effect. 

# Simulation 17

## Number of fledgling as the response (Poisson)

```{r TESB, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[17]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Overall, I wouldn't say there's a clear superior model when considering multiple selection criteria. 

We now also need to check model assumptions and diagnostics.

```{r ANH, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our k-indices are okay. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r TLJ, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r TFA, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[17]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

The model only fitting territory as a random effect seems to perform well enough on the criteria when compared to the other models. 

We now also need to check model assumptions and diagnostics. 

```{r Rogue, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices seem okay. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. None of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r ROTJ, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Solo, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[17]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

While the BIC of the territory only model is worse than the BIC of the band ID only model, the band ID only model's adjusted $R^2$ is so much lower that I probably wouldn't recommend it.

We now also need to check model assumptions and diagnostics.

```{r ROTS, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r TROS, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 17

```{r Mando, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[17], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[17], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[17], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[17], 3))
print(string)
```
That mate fidelity probability is pretty low, but so is the female dispersal probability. 

# Simulation 18

## Number of fledgling as the response (Poisson)

```{r 1, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[18]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Based on the output above, I would recommend the band ID only model.  

We now also need to check model assumptions and diagnostics.

```{r 2, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r 3, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r 4, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[18]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics. 

```{r 5, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. diagnostics look okay. 

```{r 6, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r 7, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[18]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Honestly, model selection here is a bit of a tossup.  

We now also need to check model assumptions and diagnostics.

```{r 8, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. 

```{r 9, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 18

```{r 10, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[18], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[18], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[18], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[18], 3))
print(string)
```
Extremely high probability of mate fidelity. 

# Simulation 19

## Number of fledgling as the response (Poisson)

```{r Abbey Road, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[19]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Bird ID model seems to perform well enough on the criteria. 

We now also need to check model assumptions and diagnostics.

```{r Rubber Soul, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r White Album, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Revolver, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[19]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Based on the output above, I would recommend fitting band ID as a random effect and maybe territory.

We now also need to check model assumptions and diagnostics. 

```{r Let It Be, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices look good. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. None of the diagnostic plots seem to suggest gross violations of assumptions. 

```{r Sgt Peppers, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Hard Day's Night, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[19]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Each model has criteria they perform well on and one they don't. 

We now also need to check model assumptions and diagnostics.

```{r Help, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Magical Mystery Tour, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 19

```{r Please Please Me, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[19], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[19], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[19], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[19], 3))
print(string)
```
Once again, we see a high mate fidelity probability and a difficulty detecting the territory effect. 

# Simulation 20

## Number of fledgling as the response (Poisson)

```{r red, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[20]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
The territory model is performing very well (comparatively) on AIC and $R^2$ and is doing okay on BIC. 

We now also need to check model assumptions and diagnostics.

```{r purple, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps moderately concerning.

```{r yellow, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r green, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[20]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

Based on the output, I would recommend fitting territory as a random effect and maybe band ID as well. 

We now also need to check model assumptions and diagnostics. 

```{r orange, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. Diagnostics look mildly concerning. 

```{r pink, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r blue, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[20]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Since the model fitting both isn't performing well on AIC and BIC, I would recommend the model that only fits territory as a random effect. 

We now also need to check model assumptions and diagnostics.

```{r black, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r white, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 20

```{r brown, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[20], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[20], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[20], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[20], 3))
print(string)
```
# Simulation 21

## Number of fledgling as the response (Poisson)

```{r Rancor, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[21]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Territory model is best on all criteria. 

We now also need to check model assumptions and diagnostics.

```{r Summa verminoth, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful, except for the band ID only model.

```{r Massiff, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Krayt dragon, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[21]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

The territory only model performs well enough in all criteria. 

We now also need to check model assumptions and diagnostics. 

```{r Wampa, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. The diagnostic plots look okay. 

```{r Acklay, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Colo clawfish, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[21]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

Similar to the previous batch of models. 

We now also need to check model assumptions and diagnostics.

```{r Reek, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Rathtar, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 21

```{r Nexu, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[21], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[21], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[21], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[21], 3))
print(string)
```
This run was designed to allow for the territory effect to be present. 

# Simulation 22

## Number of fledgling as the response (Poisson)

```{r Rey, comment = NA, echo = FALSE}

form.list=list(as.formula(Fledge~
                          # this is what can be switched up
                            s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")),
               
                as.formula(Fledge~
                          # this is what can be switched up 
                            s(Yr, bs = "cc", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Fledge~
                             s(Yr, bs = "cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

pois.summary.results=list()
pois.smooth.results=list()
pois.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[22]],method="REML",family=poisson)
  models[[i]] <- mod
  # gather results & add labels
  pois.summary.results[[i]]=glance(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  pois.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Poisson",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

pois.summary.tbl=do.call('rbind',pois.summary.results) %>% arrange(AIC)
pois.smooth.tbl=do.call('rbind',pois.smooth.results)
pois.fixed.tbl=do.call('rbind',pois.fixed.results)

kable(pois.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(pois.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(pois.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```
Overall, I wouldn't say there's a clear superior model when considering multiple selection criteria. 

We now also need to check model assumptions and diagnostics.

```{r Finn, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. The diagnostic plots for the models are perhaps mildly concerning, but not awful.

```{r Porgs, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Z-score number of fledgling (Gaussian)

```{r Jakku, comment = NA ,echo = FALSE}
form.list=list(as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(Terrs,bs="re")),
               
               as.formula(z_score~
                            s(Yr,bs="cc", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

z.summary.results=list()
z.smooth.results=list()
z.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[22]],method="REML")
  models[[i]] <- mod
  # gather results & add labels
  z.summary.results[[i]]=glance(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
  z.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Gaussian",RE=ifelse(i==1,"BandID",ifelse(i==2,"Terr","BandID+Terr")))
}

z.summary.tbl=do.call('rbind',z.summary.results) %>% arrange(AIC)
z.smooth.tbl=do.call('rbind',z.smooth.results)
z.fixed.tbl=do.call('rbind',z.fixed.results)

kable(z.summary.tbl,caption="Z-score GAMMs summary table.")
kable(z.smooth.tbl,caption="Z-score GAMMs smooth terms table.")
kable(z.fixed.tbl,caption="Z-score GAMMs linear terms table.")

```

I would recommend fitting both REs based on the output above. 

We now also need to check model assumptions and diagnostics. 

```{r Poe Dameron, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```

Our k-indices are still on the smaller side, but are better than those seen in the models fit with other response variables. The edf on the year term suggests that it is being shrunk out of the model, which is expected since the z-scores are calculated to remove the year effect. Diagnostics look okay(ish).

```{r BB-8, comment = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Eggs (Binomial)

```{r Holdo, comment = NA, echo = FALSE}

form.list=list(as.formula(Eggs~
                          # this is what can be switched up
                            s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")),
               
                as.formula(Eggs~
                          # this is what can be switched up 
                            s(Yr, bs = "cr", k = 15)+s(Terrs,bs="re")),
               
                as.formula(Eggs~
                             s(Yr, bs = "cr", k = 15)+s(birdID,bs="re")+s(Terrs,bs="re")))

binom.summary.results=list()
binom.smooth.results=list()
binom.fixed.results=list()
models <- list()
for(i in 1:length(form.list)){
  # fit model
  mod=gam(form.list[[i]],data=df_list[[22]],method="REML",family=binomial)
  models[[i]] <- mod
  # gather results & add labels
  binom.summary.results[[i]]=glance(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.smooth.results[[i]]=tidy(mod) %>% add_column(Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
  binom.fixed.results[[i]]=cbind.data.frame(summary(mod)$p.table,Family="Binomial",RE=ifelse(i==1,"BirdID",ifelse(i==2,"Terr","BirdID+Terr")))
}

binom.summary.tbl=do.call('rbind',binom.summary.results) %>% arrange(AIC)
binom.smooth.tbl=do.call('rbind',binom.smooth.results)
binom.fixed.tbl=do.call('rbind',binom.fixed.results)

kable(binom.summary.tbl,caption="No. fledge GAMMs summary table.")
kable(binom.smooth.tbl,caption="No. fledge GAMMs smooth terms table.")
kable(binom.fixed.tbl,caption="No. fledge GAMMs linear terms table.")
```

I would recommend fitting band ID in the model and maybe territory as well based on the output. 
We now also need to check model assumptions and diagnostics.

```{r Crait, comment = NA, echo = FALSE}
k.check(models[[1]])
k.check(models[[2]])
k.check(models[[3]])
```
Our K indices are smaller than one would hope for. However, the diagnostic plots don't seem terribly unreasonable. However the QQ plot for the model that fits both REs (the third one) does look a bit worse, so I would maybe consider the models that only fit only one RE.

```{r Maz Kanata, commet = NA, echo = FALSE}
appraise(models[[1]], method = "simulate")
appraise(models[[2]], method = "simulate")
appraise(models[[3]], method = "simulate")
```

## Probabilites used to generate simulation 22

```{r Scavenger, comment = NA, echo = FALSE}
string <- paste0("This dataset was generated with a probability of mate fidelity of ", round(probs$pFidel[22], 3), 
                 ", a probability of pair dispersal of ", round(probs$pDispP[22], 3), 
                 ", a probability of single male dispersal of ", round(probs$pDispM[22], 3), 
                 ", and a probability of single female dispersal of ", round(probs$pDispF[22], 3))
print(string)
```
This run was generated to make it difficult to detect the territory effect. 












